---
title: "formative.rmd"
author: "yq2205"
date: "10/5/2017"
output: html_document
---

```{r}
install.packages("tidyr", "dplyr")
library(tidyr, dplyr)
```


#4.Upload the MITx/Harvardx dataset to R as a dataframe named D1(Please inlcude your code in your markdown document)
```{r }
  D1 <- read.csv("HMXPC13_DI_v2_5-14-14.csv", sep = ",", header = TRUE)

```

#5. What does the DI suffix that is appeneded to two of the variable names mean?
#ANSWER 5:DI is the identifier to refer to a feature. (?not sure)

#6. How many people enrolled in HarvardX/CS50x recieved certification in 2012? (Please inlcude your code in your markdown document)
#ANSWER 6: 1,287 observations
```{r}
A6 <- dplyr::filter(D1, course_id == "HarvardX/CS50x/2012" , certified =="1")
```


#7.How many people registered for HarvardX/CS50x from Columbia on October 15, 2012? (Please inlcude your code in your markdown document)
#ANSWER 7: O observation
```{r}
A7 <- dplyr::filter(D1, course_id == "HarvardX/CS50x", final_cc_cname_DI == "Columbia",  start_time_DI=="2012_10_15")
```


#8.Create a new data frame (D2) that includes student ID and registration date for all students from a country of your choice (Please inlcude your code in your markdown document)
```{r}
A8 <- dplyr::filter(D1, final_cc_cname_DI=="Japan")
D2<-dplyr::select(A8, "userid_DI", "start_time_DI")

```

#9. Create a new data frame (D3) in which the column names are the registration dates, with one column containing the student ids and all other cells indicating a 1 if the student registered on that date or an NA if they did not (hint: you will need to create a new variable before you change the structure of your data frame)
```{r}
A9<- dplyr::select(D1, "start_time_DI","userid_DI", "registered")
D3<-tidyr::spread(A9,unique("start_time_DI"),"userid_DI", "registered" )

```


#10. Now make the row names of D3 the student ids on your new data frame and remove the user id column from your data frame
```{r}

```

#11. Convert your data frame to a matrix (M1)
```{r}
M1
```

#12. Create a new matrix which is the transposed version of your matrix (M2)
```{r}
M2
```

#13. Create a third matrix (M3) that is a student by student matrix where the cells in the matrix represent if two studentes registered on the same day (This will take a lot of processing power, you may not be able to complete it if you have a large number of students)
```{r}
M3
```


#14. Convert the diagonal of your matrix into NAs
```{r}
diag()<-NA
```

